Edge sign prediction in general graphs and Correlation Clustering

### 2017-08-24 cc/cc_main.tex
change intro of CC

In this section, we introduce the \pcc{} problem (\autoref{sub:problem_setting}) and motivate it
both by general applications (\autoref{ssub:cc_applications}) and by its close connection with the
\esp{} problem (\autoref{sub:relation_with_edge_sign_prediction}). After discussing its theoretical
complexity and various approximation methods (\autoref{ssub:cc_harness_approx}) along other kinds of
methods (\autoref{ssub:cc_methods}), we will review related problems stemming from the original
formulation (\autoref{sub:variants_and_extensions}). In doing so, we present a thorough and updated
counterpart to existing surveys the same
topic~\autocites{bonchi2014correlation}{surveyCC16}{CCWirth2017}.

@@

\subsection{Problem setting and applications}
\label{sub:problem_setting}
\input{cc_problem_applications}

\subsection{Relation with edge sign prediction}
\label{sub:relation_with_edge_sign_prediction}
\input{cc_sign_relation}

>>>>

As mentioned earlier, most real signed graphs are not fully balanced and thus do not have a
perfectly consistent clustering. The problem of quantifying how much a given graph departs from this
ideal situation is called \pcc{}. After defining it formally in \autoref{sub:problem_setting}, we
show that \pcc{} is a learning problem on its own, and discuss how it relates to the binary
classification problem of predicting edge signs, among many others applications. We then present
numerous methods to solve \pcc{} in \autoref{sub:state_of_the_art}, ranging from exact methods (that
implicitly leverage our bias) to heuristics (whose greedy and energy minimization frameworks are
classic in unsupervised graph cut problems). We also devote a large section to approximation
methods, in order to get a sense of why the problem is \NPc{}. This allows us to finish in
\autoref{sub:cc_non_worst_case} by describing situations related to our bias where is possible to
solve the problem efficiently and optimally. By doing so, we update existing surveys on the same
topic~\autocites{bonchi2014correlation}{surveyCC16}{CCWirth2017}, highlighting the importance of
\pcc{} to solve our binary learning problem.

@@

\subsection{Problem setting and connection to \esp{}}
\label{sub:problem_setting}
\input{cc_problem_applications}

### 2017-08-24 cc/cc_problem_applications.tex
change intro of CC

Now consider a clustering \cluster{} of $V$, that is a function from $V$ to $\Nbb{}^{|V|}_{>0}$
that assigns to each node a cluster index.\marginpars{We will also abuse the notation and let
\cluster{} be a set of clusters $\cluster=\{C_1, C_2, \ldots, C_k\}$ that form a partition of $V$.
That is, $\forall i\,C_i\subset V$, $\bigcup_{i=1}^k C_i = V$ and $\forall i\neq j,\, C_i\cup C_j =
\emptyset$.} For instance, $\cluster(u) = 3$ means that $u$ belongs
to the third cluster. We can evaluate how \cluster{} fits our clustering paradigm in two ways,
either by the number of \emph{agreements}, that is the weighted number of positive edges inside
clusters plus the weighted number of negative edges across clusters; or by the number of
\emph{disagreements}, that is the weighted number of negative edges inside clusters plus the
weighted number of positive edges across clusters. Given a cost function $c$, which is usually the
identity, \pcc{} can then be seen as a graph optimization problem, either of maximizing agreements
(\maxa{}):
\begin{equation}
	\max_{\cluster{}} \sum_{\cluster(u) = \cluster(v)} c(w_{uv}^+) +
	\sum_{\cluster(u) \neq \cluster(v)} c(w_{uv}^-)
	\label{eq:maxa}
\end{equation}
or minimizing disagreements (\mind{})\footnote{Note that in the data mining literature, \pcc{} may
refer to another problem. Namely, it is a special case of high-dimensional data clustering, where
features are locally correlated in various ways across different clusters that reside in arbitrarily
oriented subspaces~\autocite{otherCCproblem09}.}:
\begin{equation}
	\min_{\cluster{}} \sum_{\cluster(u) = \cluster(v)} c(w_{uv}^-) +
	\sum_{\cluster(u) \neq \cluster(v)} c(w_{uv}^+)
	\label{eq:mind}
\end{equation}

Although an optimal clustering $\cluster^\star$ achieves the same value on both \eqref{eq:maxa}
and \eqref{eq:mind}, we will see in \autoref{sub:state_of_the_art} that the latter objective is in
some sense \enquote{easier}. Another interesting feature of the \pcc{} problem is that contrary to
other clustering formulations, it does not require us to set the number of clusters $k$ beforehand.
Instead, $k$ emerges as a natural property of the solution. Since clustering is an unsupervised
problem, this is generally handy. However, in some situations, we may have prior knowledge on how
many clusters are the data, or external constraints. This can be handled with parametrized version
of \pcc{}, namely \maxa$[k]$ and \mind$[k]$ where the optimization is over clustering with exactly
$k$ clusters.

@@

\subsubsection{Applications}
\label{ssub:cc_applications}

>>>>

%TODO replace N by [|K|] (and define that notation in the table)

Now consider a clustering \cluster{} of $V$, that is a function from $V$ to $\Nbb{}^{|V|}_{>0}$ that
assigns to each node a cluster index. For instance, $\cluster(u) = 3$ means that $u$ belongs to the
third cluster. We will also abuse the notation and let \cluster{} be a set of clusters $\{C_1, C_2,
\ldots, C_K\}$ that form a partition of $V$.\footnote{That is, $\forall i\,C_i\subset V$,
$\bigcup_{i=1}^K C_i = V$ and $\forall i\neq j,\, C_i\cap C_j = \emptyset$.}
We can evaluate how \cluster{} fits our clustering paradigm in two ways,
either by the number of \emph{agreements}, that is the weighted number of positive edges inside
clusters plus the weighted number of negative edges across clusters; or by the number of
\emph{disagreements}, that is the weighted number of negative edges inside clusters plus the
weighted number of positive edges across clusters. Given a cost function $c$, which is usually the
identity, \pcc{} can then be seen as a graph optimization problem, either of maximizing agreements
(\maxa{}):
\begin{equation}
	\max_{\cluster{}} \sum_{\cluster(u) = \cluster(v)} c(w_{uv}^+) +
	\sum_{\cluster(u) \neq \cluster(v)} c(w_{uv}^-)
	\label{eq:maxa}
\end{equation}
or minimizing disagreements (\mind{})\footnote{Note that in the data mining literature, \pcc{} may
refer to another problem. Namely, it is a special case of high-dimensional data clustering, where
features are locally correlated in various ways across different clusters that reside in arbitrarily
oriented subspaces~\autocite{otherCCproblem09}.}:
\begin{equation}
	\min_{\cluster{}} \sum_{\cluster(u) = \cluster(v)} c(w_{uv}^-) +
	\sum_{\cluster(u) \neq \cluster(v)} c(w_{uv}^+)
	\label{eq:mind}
\end{equation}

Although an optimal clustering $\cluster^\star$ achieves the same value on both \eqref{eq:maxa}
and \eqref{eq:mind}, we will see in \autoref{sub:state_of_the_art} that the latter objective is in
some sense \enquote{easier}. Another interesting feature of the \pcc{} problem is that contrary to
other clustering formulations, it does not require us to set the number of clusters $K$ beforehand.
Instead, $K$ emerges as a natural property of the solution. Since clustering is an unsupervised
problem, this is generally handy. However, in some situations, we may have prior knowledge on how
many clusters are the data, or external constraints. This can be handled with parametrized version
of \pcc{}, namely \maxa$[K]$ and \mind$[K]$ where the optimization is over clustering with exactly
$K$ clusters.

@@

\subsubsection{Connection with \esp{} and other applications}
\label{ssub:cc_applications}
